Using IRS Data to Predict Electric Vehicle Count

### 2024-08-06 code/eda-code/eda-ev-dataset.qmd
add updated models, manuscript, and final report

```{r}
# Import Data, Check Descriptive Statistics & Data Types
data_location <- here::here("starter-analysis-exercise","code","final_project","Electric_Vehicle_Population_Data.csv")
ev_data <- read.csv(data_location)
summary(ev_data)
dplyr::glimpse(ev_data)
```

>>>>

```{r}
# Import Data, Check Descriptive Statistics & Data Types
data_location <- here::here("data","raw-data","Electric_Vehicle_Population_Data.csv")
ev_data <- read.csv(data_location)
summary(ev_data)
dplyr::glimpse(ev_data)
```

### 2024-08-06 products/manuscript/Manuscript.qmd
add updated models, manuscript, and final report

---
title: "Example Manuscript Template for a Data Analysis Project"
subtitle: ""
author: Sri Lakshmi Chundru, Collin Real, Joaquin Ramirez, Seth Harris
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(here)
library(knitr)
```
Data Sources for the work:

-   https://www.google.com/publicdata/directory
-   https://www.data.gov/
-   https://github.com/awesomedata/awesome-public-datasets
-   https://registry.opendata.aws/
-   https://www.kaggle.com/datasets/jainaru/electric-vehicle-population

# Summary/Abstract
_Write a summary of your project._

@@

# Data set Analysis 
```{r}
data_location <- here::here("data","raw-data","Electric_Vehicle_Population_Data.csv")
data <- read.csv(data_location)
output <- capture.output(str(data))
cat(output[1:3], sep="\n")
head(data)
summary(data)
colSums(is.na(data))
```

@@

**Geospatial Analysis (if applicable):**

- Use geographic mapping tools to identify clusters or patterns in vehicle registrations.

@@

**Statistical Model**
- First iteration of models
- Produced a few statistically significant tax metrics for predicting the number of EVs in a given county
- Washington demographics datasets could further enhance our analysis

>>>>

---
title: "Using IRS Data to Predict Electric Vehicle Count"
subtitle: ""
author: Sri Lakshmi Chundru, Collin Real, Joaquin Ramirez, Seth Harris
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

# Summary/Abstract

@@

# Data set Analysis 
```{python}
import pandas as pd
pd.set_option('display.max_rows', None)

# Load the dataset
data = pd.read_csv('../../data/processed-data/brand_model_year_tax_data.csv').drop(
    [
        'The State Federal Information Processing System (FIPS) code',
        'The State associated with the ZIP code',
        'Number of returns [3]'
    ],
    axis = 1
)
data.head(10)
```

@@

@@

**Statistical Model**
- First iteration of models
- Produced a few statistically significant tax metrics for predicting the number of EVs in a given zip code
- Washington demographics datasets could further enhance our analysis
